---
title: "Software in Soton Results - HPC use by faculty breakdown"
author: "Richard J. Acton"
date: "`r Sys.Date()`"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float: no
    df_print: paged
  html_notebook:
    fig_caption: yes
    number_sections: yes
    toc: yes
    toc_float: no
  pdf_document:
    toc: yes
    fig_caption: yes
    df_print: kable
bibliography: "`r normalizePath(params$bib)`"
csl: "`r normalizePath(params$csl)`"
link-citations: yes
linkcolor: blue
#runtime: shiny
editor_options: 
  chunk_output_type: inline
params:
  bib: "~/Documents/bibtex/library.bib"
  csl: "~/Documents/bibtex/genomebiology.csl"
  pwd: "~/Documents/jobs/soton_software_survey_analysis_2019/"
---

# Introduction

# Set-up

## Libs

```{r libs}
suppressPackageStartupMessages({
  library(tidyverse)
  library(plotly)
})
```

## Env

```{r env}
knitr::opts_knit$set(root.dir = normalizePath(params$pwd))
setwd(params$pwd)
```

# Data Read-in

```{r}
softInSoton <- read_csv("./data/Cleaning-of-Uni-Soton-Software-Survey-26Jun19.csv")
Nrespondants <- softInSoton %>% nrow()
dim(softInSoton)
colnames(softInSoton)
```

Estimated staff by faculty:

| faculty | % respondants | % total |
|-|-|-|
| Engeneering | 43 | 10 |
| life sciences | 23 | 11 |
| medcine | 15 | 10 |
| social sciences | 13 | 8 |
| arts | 7 | 8 |

[From Simon Hettricks Slides](https://slides.com/simonhettrick/software-in-southampton#/3/2)

```{r}
transforms <- 
softInSoton %>%
  group_by(`In which faculty are you based?`) %>%
  summarise(n=n()) %>%
  mutate(percentRespondants = (n / Nrespondants) * 100) %>%
  mutate(
    scaledByFaculty = c(0.08,0.1,0.11,0.1,0.08),
    estimatedStaff = n * (1 / scaledByFaculty)
  )

transforms
```

# Grouping Responses

```{r}
softInSoton %>%
  distinct(`Have you used IRIDIS, the University's high-performance computing (HPC) system?`)
```

```{r}
softInSotonGrouped <- 
softInSoton %>%
  select(
    `In which faculty are you based?`,
    `Have you used IRIDIS, the University's high-performance computing (HPC) system?`
  ) %>%
  # Grouping responses
  rename(iridisUse = `Have you used IRIDIS, the University's high-performance computing (HPC) system?`) %>%
  mutate(
    iridisUseGrouped = case_when(
      iridisUse == "N/A" ~ as.character(NA),
      # future
      iridisUse %in% c(
        "No, but I may like to use IRIDIS in the future",
        "No, but I would like to use IRIDIS in the future",
        "No, but I *might* like to use IRIDIS in the future",
        "No requirement yet but it may arise in the future",
        "No, I'm not sure if I'll need to yet"
      ) ~ "Potential Future User",
      iridisUse %in% c(
        "No, I do not require HPC in my research",
        "I do not run computational modelling any more.",
        "I have used Lyceum before, but for undergraduate work"
      ) ~ "No - Not required / no longer used",
      iridisUse %in% c(
        "No, I have not used HPC facilities myself, but do I use data from simulations run using the NOCS HPC system", 
       "My PhD students have used it",
       "PhD students have",
       "My students have",
       "My collaborators have used IRIDIS and other HPC facilities in projects we collaborate on",
       "I haven't but my students and postdocs have",
       "used to process my data but not by me"
      ) ~ "Used on my behalf / in collaboration with",
      iridisUse %in% c(
        "No, I have not used HPC facilities myself, but do I use data from simulations run using the NOCS HPC system", 
       "I have access to it but I am using other HPC facilities for now, still have to migrate to IRIDIS.",
       "No, I use other HPC facilities",
       "Too little memory"
      ) ~ "Uses other facilities",
      TRUE ~ iridisUse
    )
  ) 
```

## Response Counts

```{r}
softInSotonGroupedCounts <- 
softInSotonGrouped %>% 
  group_by(`In which faculty are you based?`) %>%
  mutate(Nbyfaculty = n()) %>%
  group_by(iridisUseGrouped, `In which faculty are you based?`) %>%
  summarise(
    N = n(), 
    percentFaculty = (N/Nbyfaculty[1]) * 100,
    Nbyfaculty = Nbyfaculty[1]
  ) %>%
  left_join(
    .,
    transforms %>% select(`In which faculty are you based?`, scaledByFaculty),
    by = "In which faculty are you based?"
  ) %>%
  mutate(extrapolatedN = N * (1/scaledByFaculty))


softInSotonGroupedCounts
```

```{r}
barchart <- function(df,yvar){
    plot <- ggplot(df,aes(`In which faculty are you based?`,!!sym(yvar))) + 
    #ggplot(.,aes(`In which faculty are you based?`)) + 
    #geom_histogram(
      #stat = 'count',
    geom_col(
      position ='dodge',
      aes(
        fill = iridisUseGrouped,
        text = paste0(
          "Faculty Counts: ", df$N, " / ", df$Nbyfaculty," (",sprintf("%.2g",df$percentFaculty),"%)\n",
          "Extrapolated Number of Staff: ", sprintf("%.0f",df$extrapolatedN) , "\n",
          "Faculty: ", df$`In which faculty are you based?`,"\n",
          "Use: ", df$iridisUseGrouped
        )
      )
    ) + 
    theme(
      axis.text.x = element_text(angle = 30),
      legend.position = "bottom"
    )
}
```

# Results

```{r,fig.width=12,fig.asp=9/16}
barchart(softInSotonGroupedCounts, "percentFaculty") %>%
    ggplotly(dynamicTicks = TRUE, tooltip = "text")
```

```{r,fig.width=12,fig.asp=9/16}
barchart(softInSotonGroupedCounts, "extrapolatedN") %>%
    ggplotly(dynamicTicks = TRUE, tooltip = "text")
```

Considering users expressing an interest in future use, users of other factilities and users who work with others who use HPC on their behalf I estimate 64-109 potential users in Environmental and life-sciences, 10-20 potential users in medicine, 320-450 in Engeneering and physical sciences, 50-62 potential users in Social Sciences and ~12 in the arts and humanities

# Session Info

```{r sessionInfo}
sessionInfo()
```

# References

<div id = "refs"></div>
